%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Network Analyst} % Job title
    {SmithGroup} % Organization
    {Ann Arbor, MI} % Location
    {May 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Own multiple IT systems, including the following: networking/server/backup/UPS infrastructure, CUCM/CUC/Expressway, Webex, MS Teams, Azure AD, Exchange,  ADFS, Data Center Expert, and SCCM}
        \item {Contribute to development of in-house Azure applications}
        \item {Mentor local IT staff on technical/networking concepts and procedures}
        \item {Create and maintain documentation for IT and end user systems and processes}
        \item {Collaborate with IT managers to recognize inefficiencies and facilitate continuous improvement}
        \item {Research, plan, and draft proposals for required system additions and upgrades}
        \item {Plan maintenance windows for production environments and services}
        \item {Configure and maintain network infrastructure at the access, distribution, and core layers}
        \item {Perform root cause analysis at the device, network, and application levels}
        \item {Standardize and maintain infrastructure configuration via CLI}
        \item {Support Cisco Call Manager/Unity Connection for VoIP, unified messaging, overhead paging, and voicemail}
        \item {Monitor aggregate service and network health via Solarwinds}
        \item {Developed and automated process to upload 80TB+ of project data to the cloud after ransomware attack}
        \item {Redesigned and rebuilt enterprise network/server/security architecture from scratch after ransomware attack}
        \item {Managed integration of multiple AD/DNS/email/collaboration environments from mergers and acquisitions}
        \item {Migrated 14 offices to a globalized E.164 dial plan to simplify routing and administration}
        \item {Authored and maintained Python modules leveraging APIs to automate repetitive tasks}
        \item {Planned and executed migration from CMS to Webex for enterprise video conferencing}
        \item {Planned and executed migration from CUCM to MS Teams for enterprise calling}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Systems Architect} % Job title
    {Wroble Systems Design} % Organization
    {Ann Arbor, MI} % Location
    {May 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design, deploy, and support enterprise systems based on client needs including:}
        \item {Active Directory/Azure AD Connect}
        \item {Office 365/Exchange}
        \item {DNS/ADFS/PKI/KMS/DHCP}
        \item {Collaboration suites (CUCM/Webex/Teams/Zoom)}
        \item {Physical network (rack/routers/switches/servers/ISP/cabling)}
        \item {Logical network (VLAN/IP addressing/VPN/security)}
        \item {Cloud services (SaaS/PaaS/IaaS)}
        \item {Perform preventative maintenance as well as break/fix support}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network Engineer/Senior Systems Architect} % Job title
    {Plasan Carbon Composites} % Organization
    {Walker, MI} % Location
    {April 2015 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched classification algorithms(SVM, CNN) to improve accuracy of human exercise recognition with wearable device.}
        \item {Developed two TIZEN applications to collect sample data set and to recognize user exercise on SAMSUNG Gear S.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Security Researcher (Compulsory Military Service)} % Job title
    {R.O.K Cyber Command, MND} % Organization
    {Seoul, S.Korea} % Location
    {Aug. 2014 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
        \item {Implemented a distributed web stress test tool with high anonymity.}
        \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Game Developer Intern at Global Internship Program} % Job title
    {NEXON} % Organization
    {Seoul, S.Korea \& LA, U.S.A} % Location
    {Jan. 2013 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market.}
        \item {Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic and designed game graphics.}
        \item {Won the 2nd prize in final evaluation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher for <Detecting video’s torrents using image similarity algorithms>} % Job title
    {Undergraduate Research, Computer Vision Lab(Prof. Bohyung Han)} % Organization
    {Pohang, S.Korea} % Location
    {Sep. 2012 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched means of retrieving a corresponding video based on image contents using image similarity algorithm.}
        \item {Implemented prototype that users can obtain torrent magnet links of corresponding video relevant to an image on web site.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Trainee} % Job title
    {Software Maestro (funded by Korea Ministry of Knowledge and Economy)} % Organization
    {Seoul, S.Korea} % Location
    {Jul. 2012 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed research memory management strategies of OS and implemented in Python an interactive simulator for Linux kernel memory management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {ShitOne Corp.} % Organization
    {Seoul, S.Korea} % Location
    {Dec. 2011 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a proxy drive smartphone application which connects proxy driver and customer. Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Penetration Tester} % Job title
    {SAMSUNG Electronics} % Organization
    {S.Korea} % Location
    {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
        \item {Conducted penetration testing on SAMSUNG Smart TV.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
